%-------------------------
% Systems Automation & Robotics Engineer Resume
%-------------------------

\documentclass[letterpaper,10.5pt]{article}

\usepackage[
    left=0.5in,
    right=0.5in,
    top=0.45in,
    bottom=0.45in,
]{geometry}

\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\pdfgentounicode=1

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\raggedright
\raggedbottom
\setlength{\tabcolsep}{0pt}
\linespread{0.94}

% Section formatting
\titleformat{\section}
{\scshape\large}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{1.5pt}{1.5pt}

% Bullet spacing
\setlist[itemize]{
  itemsep=0.6pt,
  topsep=1pt,
  parsep=0pt,
  partopsep=0pt,
  leftmargin=12pt
}

%-------------------------
\begin{document}

\begin{center}
    \textbf{\Huge Dipesh Budhathoki} \\ \vspace{1pt}
    \small
    \href{tel:9452174344}{(945) 217-4344}
    \href{mailto:budhatdh@mail.uc.edu}{budhatdh@mail.uc.edu} \ $|$ \
    \href{https://linkedin.com/in/dipeshbudhathoki}{https://linkedin.com/in/dipeshbudhathoki} \ $|$ \
    (945) 217--4344 \ $|$ \ Cincinnati, OH
\end{center}

%-------------------------
\section{Professional Summary}
Systems Automation and Robotics Engineer with hands-on experience designing, testing, and deploying automated mechanical and electromechanical systems in manufacturing, energy, and mobility domains. Strong background in equipment design, system integration, safety-driven engineering, data-driven optimization, and field validation. Experienced working on-site with cross-functional teams to transition manual processes into scalable, automated solutions.

%-------------------------
\section{Engineering \& Automation Experience}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Procter \& Gamble — Digital Accelerator} & Cincinnati, OH \\
\textit{Research Assistant — Automation, Data \& ML Engineering} & May 2024 -- Present
\end{tabular*}

{\small
\begin{itemize}
  \item Supported manufacturing and packaging R\&D by developing automated data pipelines for production, quality, downtime, and packaging systems.
  \item Converted manual and semi-automated analytical workflows into scalable SQL and PySpark pipelines in Azure Databricks.
  \item Enabled faster equipment and process decisions by delivering integrated datasets and Power BI dashboards used by engineering and operations teams.
  \item Contributed to Physics-Informed Neural Network (PINN) models using NVIDIA PhysicsNeMo to reduce experimental downtime and improve process predictability.
  \item Operated in a fast-paced, on-site industrial environment emphasizing safety, documentation, repeatability, and stakeholder alignment.
\end{itemize}
}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{National Innovation Center (NIC)} & Kathmandu, Nepal \\
\textit{Systems Automation \& Robotics Engineer — Electric Vehicle Platforms} & May 2019 -- Nov 2020
\end{tabular*}

{\small
\begin{itemize}
  \item Led automation-focused feasibility studies converting diesel vehicles to electric systems for commercial and institutional use.
  \item Designed and integrated electric powertrains, battery enclosures, control electronics, and safety systems for rugged operating environments.
  \item Developed test benches to validate torque, voltage, thermal behavior, regenerative braking, and system reliability prior to deployment.
  \item Executed extended field trials including high-gradient routes and continuous operation, validating safety and system robustness.
  \item Delivered ROI-driven feasibility reports supporting capital funding decisions and government-backed pilot deployments.
\end{itemize}
}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Aqysta Nepal Pvt. Ltd.} & Nepal \\
\textit{Mechanical \& Automation Engineer — Sustainable Pump Systems} & Jan 2018 -- Apr 2019
\end{tabular*}

{\small
\begin{itemize}
  \item Designed and prototyped solar-integrated water pumping systems to replace manual and flow-dependent pumping operations.
  \item Integrated motors, controllers, solar panels, and mechanical structures to expand pump usability across varied terrains.
  \item Conducted multi-site installations and performance testing, improving system deployment scalability and reliability.
  \item Collaborated with suppliers, technicians, and field teams to standardize designs and installation practices.
\end{itemize}
}

%-------------------------
\section{Selected Automation \& Equipment Projects}

{\small
\begin{itemize}
  \item \textbf{Electric Safari Vehicle Automation (Government-Funded)} — Converted manual fossil-fuel safari vehicles to electric operation; achieved $\sim$90 km range with regenerative braking and validated multi-trip operation under passenger load.
  \item \textbf{Hybrid Electric Vehicle (Best Final-Year Project)} — Designed and fabricated a three-wheeled hybrid EV; performed CAD, stress analysis, powertrain sizing, and dynamic simulations.
  \item \textbf{Solar-Integrated Packaging \& Utility Equipment} — Designed modular electromechanical systems emphasizing safety, ease of installation, and operational simplicity.
\end{itemize}
}

%-------------------------
\section{Education}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{University of Cincinnati} & Cincinnati, OH \\
\textit{M.S. Mechanical Engineering (Robotics \& AI Focus)} & Aug 2023 -- Present
\end{tabular*}

{\small
\begin{itemize}
  \item Coursework: Robotics Dynamics \& Control, Decision Engineering, Kalman Filtering, AI \& Machine Learning, ROS/Gazebo
\end{itemize}
}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Institute of Engineering, Tribhuvan University} & Nepal \\
\textit{B.E. Mechanical Engineering} & Dec 2017
\end{tabular*}

{\small
\begin{itemize}
  \item Merit-based admission (Ranked 56 / 15,000+); Best Final-Year Project Award
\end{itemize}
}

%-------------------------
\section{Technical Skills}

\textbf{Automation \& Robotics:} System Integration, Electromechanical Design, Test Benches, Safety-Critical Systems \\
\textbf{Controls \& Modeling:} MATLAB, Simulink, Vehicle \& System Dynamics, Kalman Filters \\
\textbf{Manufacturing \& Packaging:} Equipment Prototyping, Field Installation, Process Optimization \\
\textbf{Data \& Software:} Python, SQL, PySpark, Azure Databricks, Power BI \\
\textbf{CAD \& Tools:} SolidWorks, Engineering Drawings, Documentation, Supplier Coordination

\end{document}
