%-------------------------
% Dense CV - Dipesh Budhathoki (Expanded & Quantified)
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[
    left=0.5in,
    right=0.5in,
    top=0.4in,
    bottom=0.4in,
]{geometry}

\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{fontawesome}
\pdfgentounicode=1

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\raggedright
\raggedbottom
\setlength{\tabcolsep}{0pt}
\linespread{1.0}

% Section formatting (tight)
\titleformat{\section}
{\scshape\raggedright\large}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{3pt}{3pt}

% Bullet spacing (tight)
\setlist[itemize]{
  itemsep=1pt,
  topsep=2pt,
  parsep=0pt,
  partopsep=0pt,
  leftmargin=18pt
}

% Custom commands
\newcommand{\cvHeading}[2]{
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2
  \end{tabular*}
}

\newcommand{\cvSubHeading}[2]{
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{#1} & \textit{#2}
  \end{tabular*}
}

%-------------------------
\begin{document}

%---------- HEADER ----------
\begin{center}
  \textbf{\Huge Dipesh Budhathoki} \\ \vspace{2pt}
  \small
  \faEnvelope\ \href{mailto:budhatdh@mail.uc.edu}{budhatdh@mail.uc.edu}
  $|$ \href{https://linkedin.com/in/dipeshbudhathoki}{linkedin.com/in/dipeshbudhathoki}
  $|$ \href{https://github.com/dipesh-158}{github.com/dipesh-158}
  $|$ Cincinnati, OH
\end{center}

%-------------------------
\section{Professional Focus}
Bridging mechanical systems, automation, and machine learning to deliver robust, validated solutions in manufacturing, mobility, and applied robotics.

%-------------------------
\section{Education}

\cvHeading{University of Cincinnati}{Cincinnati, OH} \\
\cvSubHeading{M.S. Mechanical Engineering (Robotics \& AI Focus)}{Aug 2023 -- May 2026 (Expected)}
\begin{itemize}
  \item GPA: 3.95 / 4.00
  \item Coursework: Robotics Dynamics \& Control, Introduction to Robotics, AI \& Machine Learning, Statistical Quality Control, Decision Engineering.
\end{itemize}

\cvHeading{Institute of Engineering, Tribhuvan University}{Nepal} \\
\cvSubHeading{B.E. Mechanical Engineering}{Nov 2013 -- Dec 2017}
\begin{itemize}
  \item Merit-based national admission (Ranked \textbf{56 / 15,000+} candidates)
  \item Senior Thesis: Design, Fabrication, and Testing of a 
  \href{https://www.youtube.com/watch?v=EkBO0vwB1lQ}{Three-Wheeled Hybrid Electric Vehicle}
  \item Awarded \textbf{Best Final-Year Project}
\end{itemize}

%-------------------------
\section{Publications}
\href{https://d1wqtxts1xzle7.cloudfront.net/96243500/IRJET_V9I1260-libre.pdf?1671790719=&response-content-disposition=inline%3B+filename%3DModeling_and_Performance_Analysis_of_a_C.pdf&Expires=1767394460&Signature=TKz~tHeDV3rSFWufRcahY8ITkuiY1plXaxytEr1tHz8i7jVjhPM1x3Ft9C8a3Huui71JWTcOzk7JDCHrNhyC55p7rm~~s41eGviQ3cTk5a7y2zMJ2y~yM5DCmo3JStxYRlra3coGrV81sChzB9MP4qQWhKzzRR0TZbWH8os4Ip8WS5VDTYtlmgNRoNiYSOiRz3GN-LC0plI3jy9oWk6nMzSyKA~CEG9fUM5ZJSzy94RqabLcECaKnkIuwR6aEOa0Mg53LDmKoBgvZBzpTVLT4wVAqzgmg0Vik~9hQX-wqzwIZODckKoLSpBdzngODnbr4o6BXq-W5FyLWecNROc31Q__&Key-Pair-Id=APKAJLOHF5GGSLRBV4ZA}
{Budhathoki, D., et al. \textit{Modeling and Performance Analysis of a Three-Wheeled Hybrid Electric Vehicle}.  
International Research Journal of Engineering and Technology (IRJET), Vol. 9, Issue 12, 2022. }


%-------------------------
\section{Research Experience}

\cvHeading{BEARCATs Lab, University of Cincinnati}{Cincinnati, OH} \\
\cvSubHeading{Graduate Research Assistant}{Jan 2024 -- Present}
\begin{itemize}
  \item Developing Gaussian Process Regression (GPR) models to predict knee joint torque from multi-joint gait kinematics.
  \item Achieved \textbf{$\sim$95\% predictive accuracy} on stance-phase torque estimation using limited subject-specific data.
  \item Systematically evaluated influence of kernel choice and prior information on model stability and generalization.
  \item Investigating hybrid model-based + data-driven control strategies for wearable rehabilitation robotics.
  \item Targeting reduced calibration strides and real-time inference feasibility for embedded controllers.
\end{itemize}

%-------------------------
\section{Industry \& Professional Experience}

\cvHeading{P\&G Digital Accelerator @ the University of Cincinnati}{Cincinnati, OH}
\cvSubHeading{Graduate Research Assistant — Data Engineering \& Analytics}{May 2024 -- May 2025}
\begin{itemize}
  \item Worked under industry mentorship focusing on manufacturing data engineering and analytics.
  \item Converted complex KNIME workflows into optimized SQL and PySpark pipelines in Azure Databricks.
  \item Built end-to-end ETL pipelines integrating \textbf{Production, Quality Variance, Downtime, and Packaging} datasets.
  \item Performed exploratory data analysis and feature engineering on large-scale transactional data.
  \item Identified high-downtime process orders, contributing to a documented \textbf{$\sim$20\% improvement in plant efficiency}.
  \item Developed automated workflows and Power BI dashboards to support operations and R\&D decision-making.
\end{itemize}

\cvSubHeading{Graduate Research Assistant — Deep Learning \& Physics-Informed Neural Networks}{May 2025 -- Present}
\begin{itemize}
  \item Developing hybrid deep learning frameworks integrating past experimental data with governing PDEs (rheological properties of material) using PyTorch.
  \item Implementing Physics-Informed Neural Networks (PINNs) with NVIDIA PhysicsNeMo to model physical processes.
  \item Designed custom loss functions combining data-driven and physics-based constraints, reducing required training data by \textbf{$\sim$50\%}.
  \item Evaluating model generalization, stability, and deployment feasibility for experimental process optimization.
\end{itemize}


\cvHeading{National Innovation Center (NIC)}{Kathmandu, Nepal} \\
\cvSubHeading{Research Engineer — Electric Vehicle Systems}{May 2019 -- Nov 2020}
\begin{itemize}
  \item Developed mathematical and Simulink-based models of EV powertrains for performance and energy analysis.
  \item Designed battery enclosures, motor mounts, and drivetrain layouts using SolidWorks.
  \item Built and operated test benches for torque, voltage, thermal, and regenerative braking characterization.
  \item Supported feasibility analysis for diesel-to-electric vehicle conversion projects in mountainous terrain.
\end{itemize}

\cvHeading{Aqysta Nepal Pvt. Ltd.}{Lalitpur, Nepal} \\
\cvSubHeading{Research \& Experimentation Engineer}{Jan 2018 -- Apr 2019}
\begin{itemize}
  \item Converted traditional water-wheel hydro-pumps into solar-powered pumping systems within \textbf{6 months}.
  \item Supervised installation of Barsha pumps across \textbf{20+ river sites} in Nepal.
  \item Led field testing and performance evaluation across varying flow and terrain conditions.
\end{itemize}

%-------------------------
\section{Entrepreneurship \& Leadership}

\cvHeading{Auzaar Innovation Pvt. Ltd.}{Kathmandu, Nepal} \\
\cvSubHeading{Co-Founder \& CEO}{Dec 2020 -- Aug 2023}
\begin{itemize}
  \item Led a multidisciplinary team of \textbf{5 engineers} developing EV conversion systems and agri-mechanical equipment.
  \item Secured \textbf{\$40,000+} in funding from government and non-profit research institutions.
  \item Designed and installed electric wool-ball dryers and food dehydrators across multiple deployment sites.
\end{itemize}

\cvHeading{Ministry of Social Development, Bagmati Province}{Nepal} \\
\cvSubHeading{Principal Investigator \& Mechanical Engineer}{Nov 2020 -- Sept 2022}
\begin{itemize}
  \item Converted diesel safari vehicles to electric inside Chitwan National Park.
  \item Secured \textbf{\$20,000} through the Youth Scientist Encouragement Fund.
  \item Delivered \textbf{2 fully operational EV prototypes} currently in service.
\end{itemize}

%-------------------------
%-------------------------
\section{Selected Projects}

\begin{itemize}
  \item \textbf{Autonomous Mobile Trash Collection \& Disposal Robot (ROS/Gazebo)} — 
  Designed and simulated an autonomous service robot capable of navigating a household-like environment, collecting trash, depositing it into a designated dumpster, and returning to its starting location. Implemented hybrid control using laser, IMU, and odometry sensors with reactive obstacle avoidance and path-planning comparison (with and without planning).  
  \href{https://github.com/dipesh-158/Mobile-Trash-disposal-robot}{Github}

  \item \textbf{Optimized Path Planning for Mobile Robots using Metaheuristic Algorithms} — 
  Developed a modified A*-inspired path-planning framework optimized using PSO, TLBO, Firefly Algorithm, and Biogeography-Based Optimization. Evaluated performance based on minimum distance and minimum turns in grid-based environments through extensive MATLAB simulations; demonstrated superior convergence and optimality using TLBO.  
  \href{https://github.com/dipesh-158/Optimized-pathplanning-for-mobile-robot}{Github}

  \item \textbf{Physics-Informed Deep Learning for Industrial R\&D (P\&G)} — 
  Developed hybrid PINN frameworks combining sparse sensor data with governing PDEs to model physical processes; reduced experimental data requirements by \textbf{$\sim$50\%} while maintaining model fidelity.

\end{itemize}

%-------------------------
\section{Technical Skills}

\textbf{Programming \& Data:} Python, SQL, PySpark, MATLAB, C++, Pandas, NumPy, Scikit-learn \\
\textbf{Machine Learning:} GPR, XGBoost, SHAP, PINNs, PyTorch, TensorFlow \\
\textbf{Robotics \& Control:} Kinematics, Dynamics, Kalman Filters, ROS, Gazebo \\
\textbf{Engineering Tools:} SolidWorks, ANSYS, Simulink, Azure Databricks, KNIME, Power BI, Git

%-------------------------
\section{Extracurricular Activities}

\begin{itemize}
  \item Treasurer, Graduate Student Association — Mechanical \& Materials Engineering, University of Cincinnati
  \item Active Member, International Partners \& Leaders (IPALs), University of Cincinnati
  \item Volunteer mentor for international student orientation and peer support programs
\end{itemize}

%-------------------------
\section{Certifications}

Data Scientist Nanodegree — Udacity

\end{document}
